### 2018-05-01 doc/paper.tex
Making captions prettier.
Did so by making the label bold and limiting the
captions to 75% the width of a line.

Also fixing a slight type "Casteljau" --> "de Casteljau".

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}
%% H/T: https://tex.stackexchange.com/a/244805
\usepackage{booktabs,siunitx}
%% H/T: https://tex.stackexchange.com/a/4217/32270
\usepackage{mathtools}
%% H/T: https://tex.stackexchange.com/a/33869/32270
\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/horner_inferior.pdf}
  \centering
  \caption{Comparing Horner's method to the de Casteljau method for
    evaluating \(p(s) = (2s - 1)^3\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:horner-inferior}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{../images/jlcs10_plot.pdf}
  \centering
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:jlcs-10}
\end{figure}

@@

\begin{figure}\label{fig:loc-err-accumulate}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
  \node (b0) {\(\widehat{b}^{(n)}\)}
    child {node (b1) {\(\widehat{b}^{(n - 1)}\)}
      child {node (b2) {\(\widehat{b}^{(n - 2)}\)}
        child {node (bdots) {\(\vdots\)}
          child {node (bn) {\(\widehat{b}^{(0)}\)}}
          child {node (ln) {\(\ell^{(0)}\)}}
        }
        child {node (ldots) {\(\vdots\)}}
      }
      child {node (l2) {\(\ell^{(n - 2)}\)}}
    }
    child {node (l1) {\(\ell^{(n - 1)}\)}};
  %%
  \path (b1) -- (l1) node [midway] {\(+\)};
  \path (b2) -- (l2) node [midway] {\(+\)};
  \path (bn) -- (ln) node [midway] {\(+\)};
  %% eb == exact b
  \node [right of=b0] (eb0) {\(b^{(n)}\)}
    child {node (eb1) {\(b^{(n - 1)}\)}
      child {node (eb2) {\(b^{(n - 2)}\)}
        child {node (ebdots) {\(\vdots\)}
          child {node (ebn) {\(b^{(0)}\)}}
        }
      }
    };
\end{tikzpicture}
\caption{Local round-off errors}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/compensated_insufficient.pdf}
  \centering
  \caption{Compensated Casteljau method starts to lose accuracy
    for \(p(s) = (2s - 1)^3 (s - 1)\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:compensated-insufficient}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & \widehat{b}_j^{(k)} & \widehat{\partial b}_j^{(k)} & \partial b_j^{(k)} - \widehat{\partial b}_j^{(k)} \\
    \midrule
    3 & 0 & 0.125 - 1.75 (1001 \mach) - 0.25 \mach & 0.25\mach & 0 \\
    3 & 1 & -0.125 + 1.25(1001 \mach) + 0.25 \mach & -0.25\mach & 0 \\
    3 & 2 & 0.125 - 0.75 (1001 \mach) & 0 & 0 \\
    3 & 3 & -0.125 + 0.25 (1001 \mach) & 0 & 0 \\
    \midrule
    2 & 0 & -0.5 (1001 \mach) & 3 (1001 \mach)^2 & 0 \\
    2 & 1 & 0.5(1001 \mach) + 0.125 \mach & -0.125\mach - 2 (1001 \mach)^2 & 0 \\
    2 & 2 & -0.5 (1001 \mach) & (1001 \mach)^2 & 0 \\
    \midrule
    1 & 0 & 0.0625\mach + (1001 \mach)^2 + 239\mach^2 & -0.0625\mach + 0.5  (1001 \mach)^2 - 239 \mach^2 & -5 (1001\mach)^3 \\
    1 & 1 & 0.0625\mach - (1001 \mach)^2 - 239\mach^2 & -0.0625\mach - 0.5  (1001 \mach)^2 + 239 \mach^2 & 3 (1001\mach)^3 \\
    \midrule
    0 & 0 & 0.0625 \mach & -0.0625 \mach & -4 (1001 \mach)^3 + 8 (1001 \mach)^4 \\
    \bottomrule
  \end{tabular}
  \caption{Terms computed by \texttt{CompDeCasteljau} when evaluating
    \(p(s) = (2s - 1)^3 (s - 1)\) at the point
    \(s = \frac{1}{2} + 1001 \mach\)}
  \label{tab:exact-computation}
\end{table}

@@

\begin{figure}\label{fig:error-filtration}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\widehat{\partial b}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\widehat{\partial^2 b}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\widehat{\partial^3 b}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\widehat{\partial b}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\widehat{\partial^2 b}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\widehat{\partial^3 b}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\widehat{\partial b}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\widehat{\partial^2 b}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\widehat{\partial^3 b}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\caption{Filtering errors}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/de_casteljau_smooth_drawing.pdf}
  \centering
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    in the neighborhood of its multiple root \(3/4\).}
  \label{fig:smooth-drawing}
\end{figure}

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{../images/de_casteljau_rel_error.pdf}
  \centering
  \caption{Accuracy of evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:compensated-k}
\end{figure}

>>>>

\usepackage{amsthm,amssymb,amsmath}
%% H/T: https://tex.stackexchange.com/a/202168/32270
\usepackage{textcomp}
%% H/T: https://tex.stackexchange.com/a/56877/32270
\usepackage{algorithm}
\usepackage{algpseudocode}
%% H/T: https://tex.stackexchange.com/a/244805
\usepackage{booktabs,siunitx}
%% H/T: https://tex.stackexchange.com/a/4217/32270
\usepackage{mathtools}
%% H/T: https://tex.stackexchange.com/a/33869/32270
\makeatletter
\newenvironment{breakablealgorithm}
  {% \begin{breakablealgorithm}
   \begin{center}
     \refstepcounter{algorithm}% New algorithm
     \hrule height.8pt depth0pt \kern2pt% \@fs@pre for \@fs@ruled
     \renewcommand{\caption}[2][\relax]{% Make a new \caption
       {\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}%
       \ifx\relax##1\relax % #1 is \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}%
       \else % #1 is not \relax
         \addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}%
       \fi
       \kern2pt\hrule\kern2pt
     }
  }{% \end{breakablealgorithm}
     \kern2pt\hrule\relax% \@fs@post for \@fs@ruled
   \end{center}
  }
\makeatother
%% H/T: https://tex.stackexchange.com/a/202047/32270
%%      https://tex.stackexchange.com/a/32463/32270
\usepackage[labelfont=bf]{caption}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/horner_inferior.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Comparing Horner's method to the de Casteljau method for
    evaluating \(p(s) = (2s - 1)^3\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:horner-inferior}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{../images/jlcs10_plot.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:jlcs-10}
\end{figure}

@@

\begin{figure}\label{fig:loc-err-accumulate}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
  \node (b0) {\(\widehat{b}^{(n)}\)}
    child {node (b1) {\(\widehat{b}^{(n - 1)}\)}
      child {node (b2) {\(\widehat{b}^{(n - 2)}\)}
        child {node (bdots) {\(\vdots\)}
          child {node (bn) {\(\widehat{b}^{(0)}\)}}
          child {node (ln) {\(\ell^{(0)}\)}}
        }
        child {node (ldots) {\(\vdots\)}}
      }
      child {node (l2) {\(\ell^{(n - 2)}\)}}
    }
    child {node (l1) {\(\ell^{(n - 1)}\)}};
  %%
  \path (b1) -- (l1) node [midway] {\(+\)};
  \path (b2) -- (l2) node [midway] {\(+\)};
  \path (bn) -- (ln) node [midway] {\(+\)};
  %% eb == exact b
  \node [right of=b0] (eb0) {\(b^{(n)}\)}
    child {node (eb1) {\(b^{(n - 1)}\)}
      child {node (eb2) {\(b^{(n - 2)}\)}
        child {node (ebdots) {\(\vdots\)}
          child {node (ebn) {\(b^{(0)}\)}}
        }
      }
    };
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Local round-off errors}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/compensated_insufficient.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{The compensated de Casteljau method starts to lose accuracy
    for \(p(s) = (2s - 1)^3 (s - 1)\) in the neighborhood of its
    multiple root \(1/2\).}
  \label{fig:compensated-insufficient}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & \widehat{b}_j^{(k)} & \widehat{\partial b}_j^{(k)} & \partial b_j^{(k)} - \widehat{\partial b}_j^{(k)} \\
    \midrule
    3 & 0 & 0.125 - 1.75 (1001 \mach) - 0.25 \mach & 0.25\mach & 0 \\
    3 & 1 & -0.125 + 1.25(1001 \mach) + 0.25 \mach & -0.25\mach & 0 \\
    3 & 2 & 0.125 - 0.75 (1001 \mach) & 0 & 0 \\
    3 & 3 & -0.125 + 0.25 (1001 \mach) & 0 & 0 \\
    \midrule
    2 & 0 & -0.5 (1001 \mach) & 3 (1001 \mach)^2 & 0 \\
    2 & 1 & 0.5(1001 \mach) + 0.125 \mach & -0.125\mach - 2 (1001 \mach)^2 & 0 \\
    2 & 2 & -0.5 (1001 \mach) & (1001 \mach)^2 & 0 \\
    \midrule
    1 & 0 & 0.0625\mach + (1001 \mach)^2 + 239\mach^2 & -0.0625\mach + 0.5  (1001 \mach)^2 - 239 \mach^2 & -5 (1001\mach)^3 \\
    1 & 1 & 0.0625\mach - (1001 \mach)^2 - 239\mach^2 & -0.0625\mach - 0.5  (1001 \mach)^2 + 239 \mach^2 & 3 (1001\mach)^3 \\
    \midrule
    0 & 0 & 0.0625 \mach & -0.0625 \mach & -4 (1001 \mach)^3 + 8 (1001 \mach)^4 \\
    \bottomrule
  \end{tabular}
  \captionsetup{width=.75\linewidth}
  \caption{Terms computed by \texttt{CompDeCasteljau} when evaluating \\
    \(p(s) = (2s - 1)^3 (s - 1)\) at the point
    \(s = \frac{1}{2} + 1001 \mach\)}
  \label{tab:exact-computation}
\end{table}

@@

\begin{figure}\label{fig:error-filtration}
\centering
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b\)};
    \node [box, below of=bj] (bn0) {\(\widehat{b}^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\widehat{\partial b}^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\widehat{\partial^2 b}^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\widehat{\partial^3 b}^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(\widehat{b}^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\widehat{\partial b}^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\widehat{\partial^2 b}^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\widehat{\partial^3 b}^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(\widehat{b}^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\widehat{\partial b}^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\widehat{\partial^2 b}^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\widehat{\partial^3 b}^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(\widehat{\ell}_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(\widehat{\ell}_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(\widehat{\ell}_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(\widehat{\ell}_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(\widehat{\ell}_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(\widehat{\ell}_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(\widehat{\ell}_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(\widehat{\ell}_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(\widehat{\ell}_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(\widehat{\ell}_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(\widehat{\ell}_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(\widehat{\ell}_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\captionsetup{width=.75\linewidth}
\caption{Filtering errors}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=0.9375\textwidth]{../images/de_casteljau_smooth_drawing.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    in the neighborhood of its multiple root \(3/4\).}
  \label{fig:smooth-drawing}
\end{figure}

\begin{figure}
  \includegraphics[width=0.8125\textwidth]{../images/de_casteljau_rel_error.pdf}
  \centering
  \captionsetup{width=.75\linewidth}
  \caption{Accuracy of evaluation of \(p(s) = (s - 1)\left(s - 3/4\right)^7\)
    represented in Bernstein form.}
  \label{fig:compensated-k}
\end{figure}
